Paper on the carbonate chemistry at Ny-Ålesund

### 2020-04-26 awipev-CO2.Rmd
fixed issues ph_dur

ggplotRegression <- function(fit){

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se= FALSE) +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}
```

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  # dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
  #        AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
  #        #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
  #        #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
  #        ) %>%
  # variables passed through despike with "-filtered" have been renamed without sufix.
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered, temp_sf = T_seaF)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

@@

### **seaFET calibration constante E0**

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix,
                          calT = d_all$temp_insitu_ctd_9m, calSal = d_all$sal_insitu_ctd_9m )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu_ctd_9m, calSal = d_all$sal_insitu_ctd_9m)

>>>>

ggplotRegression <- function(fit){
ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se= FALSE) +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}
```

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  # dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
  #        AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
  #        #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
  #        #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
  #        ) %>%
  # variables passed through despike with "-filtered" have been renamed without sufix.
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

@@

### **seaFET calibration constant E0**

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix,
                          calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd)
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd)

### 2020-04-26 paper.Rmd
fixed issues ph_dur

d_all <- readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
d <- d_all %>% 
  #dplyr::select
  #dplyr::filter(sal_fb > 28) %>% # remove salinity data lower than 28
  as_tsibble(index = datetime) %>% 
  dplyr::arrange(datetime) %>%
  dplyr::mutate(depth = as.numeric(str_remove(depth, pattern= " m"))) %>% #depth is a string
  fill_gaps() %>%
  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
                quarter = quarter(datetime)) %>%
  replace(., is.na(.), NA) # replace NaN by NA everywhere
tmp <- d %>% 
  as_tibble() %>% 
  dplyr::select(pH_s_seafet_temp_ctd, par_air_filtered, pco2_contros, pH_s_seafet_temp_ctd, starts_with("sal_"),
                starts_with("temp_"), at_calc, year_month, quarter)
tmp visdat::vis_miss(tmp)
gg_miss_var(tmp, facet = quarter)
```

@@

>>>>

d_all <- readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))
d <- d_all %>% 
  as_tsibble(index = datetime) %>% 
  dplyr::arrange(datetime) %>%
  fill_gaps() %>%
  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
                quarter = quarter(datetime)) %>%
  replace(., is.na(.), NA) # replace NaN by NA everywhere
```

@@

var_list <- c("sal_fb", "temp_fb")
n_na <- NULL
for (i in 1:length(var)) {
  na <- sum(!is.na([[i]]))
  a
}

pc_na <- function(x=df) {
  NAs <- as.tibble(map_df(x, function(x) sum(!is.na(x)))) %>% # number of NAs
    dplyr::select(-datetime)
  NAs <- as.data.frame(t(NAs))
  n <- nrow(x) # total number of rows
  pc_na <- n_na/n #fraction of NAs
  NAs$pc <- pc_na$V1
  return(NAs)
}
tmp <- d %>% 
  as_tibble() %>% 
  dplyr::select(pH_s_seafet_temp_ctd, par_air_filtered, pco2_contros, pH_s_seafet_temp_ctd, starts_with("sal_"),
                starts_with("temp_"), at_calc, year_month, quarter) %>%
  summarize()

tmp visdat::vis_miss(tmp)
gg_miss_var(tmp, facet = quarter)
